### 2012-12-12 counterexample to bratman on shared intention/a counterexample to bratman on shared intention.tex
working draft done

\maketitle
%\tableofcontents
\title{}

@@

The first contrast case, Gilbert's, shows that the difference can’t be just  a matter of coordination because people who merely happen to be walking side by side each other also need to coordinate their actions in order to avoid colliding.  
Note also that in both cases each individual's walking is intentional, so our intentionally walking together cannot be  only a matter of our each intentionally walking.
The second contrast case, Searle's, shows that the difference can’t just be that the resulting actions have a common effect because merely parallel actions can have common effects too.%
\footnote{
This use of contrast cases resembles \citet{Pears:1971fk}: he uses contrast cases to argue that whether something is an ordinary, individual action depends on its antecedents. 
} 
Perhaps, then, a notion of shared intention is needed to distinguish the two cases.  
Perhaps it is our acting on a shared intention that we walk together which distinguishes us from two strangers who happen to be walking side by side.%
\footnote{
Many philosophers hold that a notion of shared intention is useful for understanding acting together. 
Compare \citet[p.\ 5]{Gilbert:2006wr}: `I take a collective action to involve a collective intention.'  See also  
	\citet[p.\ 381]{Carpenter:2009wq}, 
	\citet[p.\ 369]{Call:2009fk}, 
	\citet{Kutz:2000si}, 
	\citet[p.\ 117]{rakoczy_pretend_2006} and 
	\citet{Tollefsen:2005vh}.
	}

@@

To show that  Bratman's conditions, (1)--(3), are not in fact sufficient for shared intention we need 
a case where the conditions are met and we lack a shared intention.
But how could we determine that we lack a shared intention?
As already mentioned, the notion of shared intention is supposed to 
	make it possible to 
	characterise systematically a difference between 
		cases involving shared agency (such as our walking together)
		and
		cases involving only parallel  individual agency (such as two strangers who happen to be walking the same route side-by-side). 
Suppose, then, that we had a trio of cases, A, B and C, each involving two agents.
Suppose, further, that A and B involved parallel agency only, whereas C involved shared agency.
Then we could be sure that A and B do not involve shared intention.
Now suppose 
	that, for some J, Bratman's conditions, (1)--(3) above, were met in cases B and C alike.
Suppose also that in each case, B and C, the structure of intention and knowledge mention specified by Bratman's conditions 
 played an appropriate role in guiding the agents' actions,
	and that in each case the agents did thereby  successfully J.
Finally, suppose that cases A, B and C are as similar as possible except for the differences mentioned.
Then case B would be our counterexample:
Bratman's conditions are met but there is no shared intention.
This is how our counterexample will work.
(Strictly speaking, case A is not necessary; but including it simplifies exposition.)

Several preliminaries are necessary for the construction of our counterexample. 
These preliminaries might easily give the impression that our counterexample depends on an artificial settings. 
However, having introduced the primary counterexample in an artificial setting, we will  go on to show that counterexamples can also be constructed for mundane activities including walking together.

@@

Consider the contents of the intentions concerning our J-ing in the above clauses, (1)--(3). 
What sort of activity can you intend when you intend that we J?
We cannot restrict possible values of J to activities which involve shared agency.
In imposing any such restriction we would be assuming the very notion that an account of shared intention is supposed to illuminate. 
%
%As we have stressed, 
%	make it possible to 
%	characterise systematically a difference between 
%		cases involving shared agency (such as our walking together)
%		and
%		cases involving parallel agency only (such as two strangers who happen to be walking the same route side-by-side). 
%We must therefore avoid tacitly appealing to this distinction by  restricting possible values of J to those which involve shared agency. 
Rather the above  conditions, (1)--(3), must be sufficient for shared intention even for some values of J which are `neutral with respect to shared intentionality'.%
\footnote{
 \citet[p.\ 147]{Bratman:1999fr}.
 This refines Bratman's earlier view that some admissable values of J are cooperatively neutral 
 	where an  act-type is \emph{cooperatively neutral} just if `joint performance of an act of that type may be cooperative, but it need not be' \citep[p.\ 330]{Bratman:1992mi}. 
}

To illustrate, first consider Bratman's `mafia case' where two people go to New York together by virtue of one of them forcing the other into a car and driving off \citep[p.\ 333]{Bratman:1992mi}. 
Next consider a paradigm case of where two friends cooperatively go to New York together.
It's possible to conceive of an act type of going to New York together which is broad enough that both cases, the coercive and the cooperative, fall under it.
And it's even possible to desire or intend to be involved in an act of this type.
A gangster might intend to go to New York with someone without having yet decided whether they will do this cooperatively or coercively.

@@

3$^\prime$. 1 and 2 are common knowledge between us.
\end{quote}
In defining unshared intention we have used conditions exactly like Bratman's sufficient conditions for shared intention except that Bratman's conditions have J$_1$$=$J$_2$.
At this point it might be natural for readers to suppose that agents could not have unshared intentions,
or at least that they could not do so without irrationality.
In this section we describe a possible situation in which two agents  have an unshared intention without irrationality, deception or even ignorance.
This possible situation is not the promised counterexample, but it does form the basis for it.

@@

This is not quite enough to meet the second condition, (2), because there is also a requirement about meshing subplans. 
To apply this requirement we need to generalise Bratman's definition of meshing:
\begin{quote}
`our individual subplans concerning our J-ing \emph{mesh} just in case there is some way we could J that would not violate either of our subplans but would, rather, involve the successful execution of those subplans' \citep[p.\ 106]{Bratman:1993je}.
\end{quote}
A natural generalisation is this:
\begin{quote}
our individual subplans concerning our <J$_1$, J$_2$>-ing \emph{mesh} just in case there is some way I could J$_1$ and you could J$_2$ that would not violate either of our subplans but would, rather, involve the successful execution of those subplans. 
\end{quote}
%
To illustrate, 
Ayesha's and Ahmed's subplans would fail to mesh if, in intending that they make the cross hit the red square,  Ayesha's plans had included pushing Ahmed out of the way and seizing his controls. 
They would also fail to mesh if Ayesha were planning to trick Ahmed into a situation where he would be unable to perform the actions he had been planning.
But in the case we have been describing, the agents' subplans mesh perfectly.
Each agent's subplans involve manipulating his or her own controls,
and the successes each seeks in doing this depends on the other successfully carrying out their subplans.
So Ayesha can rationally intend that they, Ayesha and Ahmed, make the cross hit the red square in accordance with and because of their intentions and meshing subplans of them.
And Ahmed likewise for making the cross hit the blue circle.

@@

In the situation just described,
Ayesha and Ahmed are playing a game and have different tasks.
Thanks to special features of the game environment, they both succeed by acting on an unshared intention.
Now compare two further players, Beatrice and Baldric, who are playing the same game. 
Their situations, knowledge states, intentions and actions are as similar as possible to Ayesha's and Ahmed's except for one detail.
Just by chance they have been assigned identical tasks: Beatrice's task is to make the cross hit the red square and Baldric's task is the same.
So where Ayesha and Ahmed have an unshared intention that they <J$_1$, J$_2$>,
Beatrice and Baldric meet Bratman's conditions (1)--(3) for having a shared intention that they J$_1$.  
But Beatrice, in planning and acting, does not rely on the coincidence of their intentions; and nor does Baldric.
(Beatrice relies on the fact Baldric intends that they J$_1$, of course; but she does not rely on the fact that Baldric intends what she intends.) 
Let us further stipulate that, due to an artefact of the way the game is structured,
the unshared intention and the 
	Bratman intention 
	\label{df:bratman_intention}
	(as we might label the structure of intention and knowledge 
	%specified in conditions (1)--(3) on page \pageref{quote:bratman_account}
	while leaving open whether it constitutes a shared intention) result in the two pairs performing same actions in the same way.
That is, Beatrice reasons about Baldric much as Ayesha reasons about Ahmed and Beatrice and does what Ayesha does; and likewise for Baldric and Ahmed.

We claim that Beatrice and Baldric have a shared intention that they J$_1$
only if 
Ayesha and Ahmed have a shared intention.%
\footnote{
Strictly speaking, 
	what matters for our argument is whether Ayesha and Ahmed have a shared intention \emph{in virtue of having the unshared intention that they <J$_1$, J$_2$>}.
	This is because, strictly speaking, we need to show, not that Beatrice and Baldric lack any shared intention whatsoever, but only that they lack a shared intention that they J$_1$ just in virtue of meeting Bratman's conditions (see (1)--(3) on page  \pageref{quote:bratman_account}). 
	For ease of exposition this is not made explicit in the main text.
} 
This claim follows from the similarities of the two cases.
The only difference is that Beatrice and Baldric happen to be assigned the same task, whereas Ayesha and Ahmed are not.
And neither Beatrice nor Baldric makes use of the fact that they have the same task. 
(This is not due to ignorance: it's just how they choose to approach their tasks.)
So if we consider  how  
		 Beatrice and Baldric's case
	differs from
		 that of Ayesha and Ahmed,
we can see that these differences do not plausibly amount to a difference with respect to shared agency.
Shared intention cannot feature in one case but not the other.

@@

But doesn't shared intention require at least this much,
that there be a single activity  about which each the agent involved has an intention? 
This might reasonably be doubted by those who, like Bratman, reject the Simple View according to which when an individual intentionally J-s she has an intention concerning her J-ing \citep{Bratman:1984jr}.
So 
	we shall not infer  that Ayesha and Ahmed lack a shared intention
	just because (by construction) there is no J such that Ayesha and Ahmed each intend that they, Ayesha and Ahmed, J.

Can we then appeal directly to intuition to show that Ayesha and Ahmed lack a shared intention?
Ayesha sees Ahmed's actions as constraints on her own, or else as opportunities.
She exploits Ahmed's intentions for her own ends.
Of course the situation is reciprocal: Ahmed exploits Ayesha in equal measure.
Each allows himself or herself to be exploited by the other because being exploited enables exploiting,
and this is the full extent of their cooperation. 
We don't suppose that reciprocal exploitation is incompatible with shared intention. 
But Ayesha and Ahmed's interaction consists entirely in this sort reciprocal exploitation, where each agent sees the other's actions only as constraints or opportunities.
Perhaps it is clear enough that 
the sort of shared agency that an account of shared intention is supposed to capture must involve more than this. 
If so, we can already claim that Ayesha and Ahmed are not acting on a shared intention.
But philosophers' intuitions about shared agency may vary, so it would be better if we could avoid such a blunt appeal to intuition.

How else could we support the claim that Beatrice and Baldric lack a shared intention? 
As mentioned at the start, 
the contrast cases are often used to anchor intuitions in theorising about shared agency.
In the next sections we shall further support our claim by contrasting Beatrice and Baldric's case with a further case, one which is as similar as possible and which does seem to involve shared agency.
The fact that Beatrice and Baldric's case contrasts with this new case will support the claim that Beatrice and Baldric lack shared intention.
This is the proximal aim of the following sections.
A more distal aim 
is to understand why Bratman's conditions are not sufficient for shared intention
and, relatedly, to provide materials for fixing his account.

\section{Individually planning all of  the agents' actions}
\label{sec:distributed_plan}

@@

Where there is an outcome and some agents each individually,
without discussion or communication,
plan for the outcome 
and where each agent has a single plan specifying roles for herself and all of the other agents,
%When there is an outcome and some agents each individually,
%without any discussion or communication,
%construct an agent-neutral plan for this outcome and then assign roles to themselves and the other agents,
we shall say that these agents each \emph{individually plan all of the agents' actions}.%
\footnote{
This phrase is ambiguous (in a way we know  no way concise of avoiding).
The idea is that each agent has a single plan in which she and  all other agents are assigned roles.
There is no requirement that any agent's plan must specify all the actions which the agents between them will perform.
}
Agents can do this by first constructing agent-neutral plans and then assigning roles to themselves and the other agents.
So, to return to our earlier example, 
 if the housemates, having decided to make a pizza, had each individually devised  agent-neutral plans for the construction of the pizza and then each individually assigned roles in their own plans to themselves and the others, 
then they would have each individually planed all of the agents' actions.

For all we have said,  agent-neutral plans might not be involved in all cases where some agents each individually plan all of the agents' actions.
We invoke agent-neutral plans only as an aid to showing that the notion of some 
agents each individually planning all of the agents' actions is theoretically coherent.

But why would some agents ever each individually plan all of the agents' actions?
One might suppose that this would occur only when each agent thinks that she in charge, or is fantasizing about controlling the others.
If you know you aren't the boss and aren't going to decide what another agent will do, why  make a plan for that agent's actions as well as your own?
Why not just plan your own actions?
As we shall now explain, 
one reason why some agents might each plan all of the agents' actions 
	even when there is manifestly no leader and the agents all have the same status
	is that doing so provides one way to solve a coordination problem.
%%having agents each individually plan all of the agents' actions
%can be a way of achieving coordination even where there is no leader and the agents all have the same status.

%How could  this work?
Sometimes a plan for your own actions needs to be constrained by, and to constrain, plans for other agents' actions.
When, for example,
you and someone else are about to move a heavy table from one room to another,
there are constraints 
on relations between
	your actions
	and
	the other's actions.
These relational constraints concern timings, forces, choices of route and more besides.
Now meeting such relational constraints does not in principle require you to plan actions other than your own.
In principle,  you  might make an initial plan for your own actions only.
You could use you initial plan to make predictions about the  other's likely actions,
and then revise this initial plan for your actions in the light of these predictions about the other's actions.
This cycle of prediction and revision might be repeated.
Your plan might also involve conditional elements to accommodate unpredicted actions.
So if you plan your own actions only,
 you will need to rely on predictions about what the other will do,
 and these predictions will sometimes depend on what you plan to do.
But there is another way to proceed,
one which avoids the need for a plan that depends on predictions which in turn depend on the plan.
For you can use the same planning processes which enable you to meet constraints on relations between two of your own actions
	in order to meet constraints on relations between your own and the other's actions.
That is, you could make a single plan for both your own and the other's actions.
(You might do this by first making an agent-neutral plan and then assigning roles.)
Making a single plan for your actions and the other's actions is a way of using your planning abilities to meet relational constraints.
Of course, 
this is only rational  if you are in a position to know that your plan for the other's actions will be sufficiently similar to her own plan for her actions.
And it is unlikely that you could know this if 
	you and the other agent differed too much in expertise,
	if there were two or more equally good ways to achieve the outcome you are planning,
	or if there were two or more equally good ways to assign roles.
But suppose that you and the other person have similar expertise in moving furniture, 
	that there is obviously exactly one most optimal route,
	 and that your positions in space manifestly determine which ends of the table you should each hold and so which role each of you should play. 
Then it is likely that you could  be in a position to know,
	even without communication,
	that your plan for the other agent's actions will nearly enough coincide with her own plan for her actions.
So  making a single plan for your actions and the other's actions can be a way of 
	working out how to 
	meet constraints on the relation between your actions and hers and so of achieving coordination.  
(Note that, as already mentioned,  we don't claim that this  is the only or best way to achieve coordination.)	
And, clearly, this applies equally to the 
 other person you are lifting the table with.
 She  could work out how to coordinate her actions with yours by likewise making a single plan for her actions and yours.%
\footnote{
As an aside, we note that 
\citet{tsai:2011_groop_effect} provide evidence indicating that planning for your own and and others' actions happens not only in conscious practical reasoning but also in planning that you may not ordinarily be directly aware of.
}

The question was why some agents would each individually plan all of the agents' actions.
We have just argued that  
one reason is that
doing this would sometimes enable the agents to solve a coordination problem.
Agents who will collaborate in an activity, such as moving a table or making a pizza, 
can sometimes individually plan all of the agents' actions,
knowing that each agent's plan is sufficiently similar to the other agents' plans.
And sometimes each can rationally perform her part in her plan for all of the agent's actions, knowing that the others will do likewise.%
\footnote{
Note that this coordination is achieved without presupposing that the agents exercise shared agency.
Of course,
	if some agents individually plan all of the agents' actions
	and then each rationally performs her part in her own plan,
	the upshot might be an exercise of shared agency.
But this shared agency is a consequence of, not a requirement on, their individually planning all of the agents' actions.
}

Now recall Beatrice and Baldric (from Section \vref{sec:the_counterexample}).
We said earlier that  they each see the other's intentions and actions  as constraints to work around or opportunities to exploit only.
This is because neither agent plans all of their actions and so neither conceives of both her own and the other's actions as parts of a single plan.
In constructing a case that contrasts with Beatrice and Baldric's we shall rely on the distinction between
a plan that includes both your own and another's actions
and 
a plan that merely exploits, and is constrained by, predictions about the other's actions.
This distinction matters independently of whether two such plans would result in different actions.
It matters because 
making a plan for your own and another's actions 
	involves changing perspective.
That is, it involves conceiving of the other's actions not only as constraints and opportunities, but as on a par with your own actions insofar as your actions and their actions are elements in a single plan directed to a single outcome.

@@

\section{Why Making One Plan or Two Matters}
The distinction between making a single plan and making two separate plans may initially seem too subtle to be useful, 
especially as 
the two separate plans may be interdependent.
Further, if two separate plans could both be executed (not just each plan but both together), then they can be combined into a single plan.
The combined plan is simply to implement each of the two formerly separate plans. 
Given these apparent grounds for scepticism,
in this section we shall explain why the distinction between making a single plan and making two separate plans matters.

***First,
the fact that two separate \emph{plans} can be combined doesn't undermine the distinction between \emph{making} a single plan and \emph{making} two separate plans.
To see why consider structure ...
[... but the really deep point is not about structure: it's about keeping plans separate meaning adopting a predictive rather than a deliberative perspective towards the actions ...]

>>>>

\maketitle
%\tableofcontents

\begin{center}
Status: unsubmitted draft, work in progress
\end{center}

@@

The first contrast case, Gilbert's, shows that the difference can’t be just  a matter of coordination because people who merely happen to be walking side by side  also need to coordinate their actions in order to avoid colliding.  
Note also that in both cases each individual's walking is intentional, so our intentionally walking together cannot be  only a matter of our each intentionally walking.
The second contrast case, Searle's, shows that the difference can’t just be that the resulting actions have a common effect because merely parallel actions can have common effects too.%
\footnote{
This use of contrast cases resembles \citet{Pears:1971fk}: he uses contrast cases to argue that whether something is an ordinary, individual action depends on its antecedents. 
} 
Perhaps, then, a notion of shared intention is needed to distinguish the two cases.  
Perhaps it is our acting on a shared intention that we walk together which distinguishes us from two strangers who happen to be walking side by side.%
\footnote{
On the idea that a notion of shared intention is useful for understanding acting together, compare  
	\citet[p.\ 381]{Carpenter:2009wq}, 
	\citet[p.\ 369]{Call:2009fk}, 
	\citet{Kutz:2000si}, 
	\citet[p.\ 175]{pacherie_framing_2011},
	\citet[p.\ 117]{rakoczy_pretend_2006}, 
	\citet{Tollefsen:2005vh},
and \citet[p.\ 5]{Gilbert:2006wr}: `I take a collective action to involve a collective intention.'  
	}

@@

To show that  Bratman's conditions, (1)--(3) \vpageref{quote:bratman_account}, are not in fact sufficient for shared intention we need 
a case where the conditions are met and we lack a shared intention.
But how could we determine that we lack a shared intention?
As already mentioned, the notion of shared intention is supposed to 
	make it possible to 
	characterise systematically a difference between 
		cases involving shared agency (such as our walking together)
		and
		cases involving only parallel  individual agency (such as two strangers who happen to be walking the same route side-by-side). 
Suppose, then, that we had a trio of cases, A, B and C, each involving two agents.
Suppose, further, that A and B involved parallel agency only, whereas C involved shared agency.
Then we could be sure that A and B do not involve shared intention.
Now suppose 
	that, for some J, Bratman's conditions, (1)--(3), were met in cases B and C alike.
Suppose also that in each case, B and C, the structure of intention and knowledge mention specified by Bratman's conditions 
 played an appropriate role in guiding the agents' actions,
	and that in each case the agents did thereby  successfully J.
Finally, suppose that cases A, B and C are as similar as possible except for the differences mentioned.
Then case B would be our counterexample:
Bratman's conditions are met but there is no shared intention.
This is how our counterexample will work.
(Strictly speaking, case A is not necessary; but including it simplifies exposition.)

%Several preliminaries are necessary for the construction of our counterexample. 
%These preliminaries might easily give the impression that our counterexample depends on an artificial settings. 
%However, having introduced the primary counterexample in an artificial setting, we will  go on to show that counterexamples can also be constructed for mundane activities including walking together.

@@

Consider the contents of the intentions concerning our J-ing in conditions (1)--(3) \vpageref{quote:bratman_account}. 
What sort of activity can you intend when you intend that we J?
Possible values of J cannot be restricted to activities which involve shared agency.
In imposing any such restriction we would be assuming the very notion that an account of shared intention is supposed to illuminate. 
%
%As we have stressed, 
%	make it possible to 
%	characterise systematically a difference between 
%		cases involving shared agency (such as our walking together)
%		and
%		cases involving parallel agency only (such as two strangers who happen to be walking the same route side-by-side). 
%We must therefore avoid tacitly appealing to this distinction by  restricting possible values of J to those which involve shared agency. 
Rather the above  conditions, (1)--(3) \vpageref{quote:bratman_account}, must be sufficient for shared intention even for some values of J which are `neutral with respect to shared intentionality.'%
\footnote{
See \citet[p.\ 147]{Bratman:1999fr}.
 This refines Bratman's earlier view that some admissable values of J are cooperatively neutral 
 	where an  act-type is \emph{cooperatively neutral} just if `joint performance of an act of that type may be cooperative, but it need not be' \citep[p.\ 330]{Bratman:1992mi}. 
}

To illustrate, first consider Bratman's `mafia case' where two people go to New York together by virtue of one of them forcing the other into a car and driving off \citep[p.\ 333]{Bratman:1992mi}. 
Next consider a paradigm case of where two friends cooperatively go to New York together.
It's possible to conceive of an act type of going to New York together which is broad enough that both cases, the coercive and the cooperative, fall under it.
And it's even possible to desire or intend to be involved in an act of this type.
As Bratman suggests,
a gangster might intend to go to New York with someone without having yet come to a view on whether this will be cooperative or coercive.

@@

3$^\prime$. 1 and 2 are common knowledge between us.
\end{quote}
In defining unshared intention we have used conditions almost exactly like Bratman's sufficient conditions for shared intention except that Bratman's conditions have J$_1$$=$J$_2$.
At this point it might be natural for readers to suppose that agents could not have unshared intentions,
or at least that they could not do so without irrationality.
In this section we describe a possible situation in which two agents  have an unshared intention without irrationality, deception or even ignorance.
This possible situation is not the promised counterexample, but it does form the basis for it.

@@

This is not quite enough to meet the second condition, (2), because there is also a requirement about meshing subplans. 
To apply this requirement we need to generalise Bratman's definition of meshing:
\begin{quote}
`our individual subplans concerning our J-ing \emph{mesh} just in case there is some way we could J that would not violate either of our subplans but would, rather, involve the successful execution of those subplans' \citep[p.\ 106]{Bratman:1993je}.
\end{quote}
A natural generalisation is this:
\begin{quote}
our individual subplans concerning our <J$_1$, J$_2$>-ing \emph{mesh} just in case there is some way I could J$_1$ and you could J$_2$ that would not violate either of our subplans but would, rather, involve the successful execution of those subplans. 
\end{quote}
%
To illustrate, 
Ayesha's and Ahmed's subplans would fail to mesh if, in intending that they make the cross hit the red square,  Ayesha's plans had included pushing Ahmed out of the way and seizing his controls. 
They would also fail to mesh if Ayesha were planning to trick Ahmed into a situation where he would be unable to perform the actions he had been planning.
But in the case we have been describing, the agents' subplans mesh perfectly.
Each agent's subplans involve manipulating his or her own controls,
and the success each seeks in doing this depends on the other successfully carrying out their subplans.
So Ayesha can rationally intend that they, Ayesha and Ahmed, make the cross hit the red square in accordance with and because of their intentions and meshing subplans of them.
And Ahmed likewise for making the cross hit the blue circle.

@@

In the situation just described,
Ayesha and Ahmed are playing a game and have different tasks.
Thanks to special features of the game environment, they both succeed by acting on an unshared intention.
Now compare two further players, Beatrice and Baldric, who are playing the same game. 
Their situations, knowledge states, intentions and actions are as similar as possible to Ayesha's and Ahmed's except for one detail.
Just by chance they have been assigned identical tasks: Beatrice's task is to make the cross hit the red square and Baldric's task is the same.
So where Ayesha and Ahmed have an unshared intention that they <J$_1$, J$_2$>,
Beatrice and Baldric meet Bratman's conditions (1)--(3) for having a shared intention that they J$_1$.  
But Beatrice, in planning and acting, does not rely on the coincidence of their intentions; and nor does Baldric.
(Beatrice relies on the fact Baldric intends that they J$_1$, of course; but she does not rely on the fact that Baldric intends what she intends.) 
Let us further stipulate that, due to an artefact of the way the game is structured,
the unshared intention and the 
	Bratman intention 
	\label{df:bratman_intention}
	(as we might label the structure of intention and knowledge 
	%specified in conditions (1)--(3) on page \pageref{quote:bratman_account}
	while leaving open whether it constitutes a shared intention) result in the two pairs performing the same actions in the same way.
That is, Beatrice reasons about Baldric much as Ayesha reasons about Ahmed, and Beatrice does what Ayesha does; and likewise for Baldric and Ahmed.

We claim that Beatrice and Baldric have a shared intention that they J$_1$
only if 
Ayesha and Ahmed have a shared intention.%
\footnote{
Strictly speaking, 
	what matters for our argument is whether Ayesha and Ahmed have a shared intention \emph{in virtue of having the unshared intention that they <J$_1$, J$_2$>}.
	This is because, strictly speaking, we need to show, not that Beatrice and Baldric lack any shared intention whatsoever, but only that they lack a shared intention that they J$_1$ just in virtue of meeting Bratman's conditions (see (1)--(3) on page  \pageref{quote:bratman_account}). 
	For ease of exposition this is not made explicit in the main text.
} 
This claim follows from the similarities of the two cases.
The only difference is that Beatrice and Baldric happen to have same task, whereas Ayesha and Ahmed have different tasks.
And neither Beatrice nor Baldric makes use of the fact that they have the same task. 
%(This is not due to ignorance: it's just how they approach their tasks.)
So if we consider  how  
		 Beatrice and Baldric's case
	differs from
		 that of Ayesha and Ahmed,
we can see that these differences do not plausibly amount to a difference with respect to shared agency.
Shared intention cannot feature in one case but not the other.

@@

But doesn't shared intention require at least this much,
that there be a single activity  about which each agent involved has an intention? 
This might reasonably be doubted by those who, like Bratman, reject the Simple View according to which when an individual intentionally J-s she has an intention concerning her J-ing \citep{Bratman:1984jr}.
So 
	we shall not infer  that Ayesha and Ahmed lack a shared intention
	just because (by construction) there is no J such that Ayesha and Ahmed each intend that they, Ayesha and Ahmed, J.

Can we then appeal directly to intuition to show that Ayesha and Ahmed lack a shared intention?
Ayesha sees Ahmed's actions as constraints to work around or  opportunities to exploit.
%She exploits Ahmed's intentions for her own ends.
Of course the situation is reciprocal: Ahmed exploits Ayesha in equal measure.
Each allows himself or herself to be exploited by the other because being exploited enables exploiting,
and this is the full extent of their cooperation. 
We don't suppose that reciprocal exploitation is incompatible with shared intention. 
But Ayesha and Ahmed's interaction consists entirely in this sort reciprocal exploitation, where each agent sees the other's actions only as constraints or opportunities.
Perhaps it is clear enough that 
the sort of shared agency that an account of shared intention is supposed to capture must involve more than this. 
If so, we can already claim that Ayesha and Ahmed are not acting on a shared intention.
But philosophers' intuitions about shared agency may vary, so it would be better if we could avoid such a blunt appeal to intuition.

How else could we support the claim that Beatrice and Baldric lack a shared intention? 
As mentioned at the start, 
the contrast cases are often used to anchor intuitions in theorising about shared agency.
In the following sections we shall further support our claim by contrasting Beatrice and Baldric's case with a further case, one which is as similar as possible and which does seem to involve shared agency.
The way that Beatrice and Baldric's case contrasts with this new case will support the claim that Beatrice and Baldric lack shared intention.
This is the proximal aim of the following sections.
A more distal aim 
is to understand why Bratman's conditions are not sufficient for shared intention
and, relatedly, to provide materials for fixing his account.

\section{Individually planning all  the agents' actions}
\label{sec:distributed_plan}

@@

Where there is an outcome and some agents each individually,
without discussion, communication or prior arrangement,
plan for the outcome 
and where each agent makes a single plan specifying roles for herself and all the other agents,
%When there is an outcome and some agents each individually,
%without any discussion or communication,
%construct an agent-neutral plan for this outcome and then assign roles to themselves and the other agents,
we shall say that these agents each 
\label{df:plan_all_actions}
\emph{individually make a plan for all the agents' actions}.%
\footnote{
This phrase is ambiguous (in a way we know  no way concise of avoiding).
The idea is that each agent makes a single plan in which she and  all other agents are assigned roles.
There is no requirement that any agent's plan must specify all the actions which the agents between them will perform.
}
%Agents can do this by first constructing agent-neutral plans and then assigning roles to themselves and the other agents.

To illustrate by returning to our earlier example, 
 if the housemates, having decided to make a pizza, had each individually devised  agent-neutral plans for the construction of the pizza and then each individually assigned roles in their own plans to themselves and the others, 
then they would have each individually made a plan for all the agents' actions.%
\footnote{
Note that, for all we have said,  agent-neutral plans might not be involved in all cases where some agents each individually make a plan for plan all the agents' actions.
We invoke agent-neutral plans only as an aid to showing that the notion of some 
agents each individually making a plan for all the agents' actions is theoretically coherent.
}
%

But why would some agents ever each individually make a plan for all the agents' actions?
One might suppose that this would occur only when each agent thinks that she in charge, or is fantasizing about controlling the others.
Fantasy aside, 
if you know you aren't in charge, why  make a plan for your own and another agent's actions?
Why not plan your own actions only?
As we shall now explain, 
one reason why some agents might each make a plan for all  the agents' actions 
	even when there is manifestly no one in charge and the agents all have the same status
	is that doing so provides one way to solve a coordination problem.
%%having agents each individually make a plan for all the agents' actions
%can be a way of achieving coordination even where there is no leader and the agents all have the same status.

%How could  this work?
Sometimes a plan for your own actions needs to be constrained by, and to constrain, plans for other agents' actions.
When, for example,
you and someone else are about to move a heavy table from one room to another,
there are constraints 
on relations between
	your actions
	and
	the other's actions.
These relational constraints concern timings, forces, choices of route and more besides.
Now meeting such relational constraints does not in principle require you to plan actions other than your own.
In principle,  you  might make an initial plan for your own actions only.
You could use your initial plan to make predictions about the  other's likely actions,
and then revise this initial plan for your actions in the light of these predictions about the other's actions.
This cycle of prediction and revision might be repeated.
Your plan might also involve conditional elements to accommodate unpredicted actions.
So if you plan your own actions only,
 you will need to rely on predictions about what the other will do,
 and these predictions will sometimes depend on what you plan to do.
But there is another way to proceed.
%one which avoids the need for a plan that depends on predictions which in turn depend on the plan.
You can use the same planning processes which enable you to meet constraints on relations between two of your own actions
	in order to meet constraints on relations between your own and the other's actions.
That is, you could make a single plan for both your own and the other's actions.
(You might do this by first making an agent-neutral plan and then assigning roles.)

Making a single plan for your own and the other's actions is a way of using your planning abilities to meet relational constraints.
Of course, 
this is only rational  if you are in a position to know that your plan for the other's actions will be sufficiently similar to her own plan for her actions.
And it is unlikely that you could know this if 
	you and the other agent differed too much in expertise,
	if there were two or more equally good ways to achieve the outcome you are planning,
	or if there were two or more equally good ways to assign roles.
But suppose that you and the other person have similar expertise in moving furniture, 
	that there is obviously exactly one most optimal route,
	 and that your positions in space manifestly determine which ends of the table you should each hold and so which role each of you should play. 
Then it is likely that you could  be in a position to know,
	even without communication,
	that your plan for the other agent's actions will nearly enough coincide with her own plan for her actions.
So  making a single plan for your actions and the other's actions can be a way of 
	working out how to 
	meet constraints on the relation between your actions and hers and so of achieving coordination.  
(Note that, as already mentioned,  we don't claim that this  is the only or best way to achieve coordination.)	
And, clearly, this applies equally to the 
 other person you are lifting the table with.
 She  could work out how to coordinate her actions with yours by likewise making a single plan for her actions and yours.%
\footnote{
As an aside, we note that 
\citet{tsai:2011_groop_effect} provide evidence indicating that making a plan for your own and and others' actions can happen not only in conscious practical reasoning but also in planning that you may not ordinarily be directly aware of.
}

The question was why some agents would each individually make a plan for all the agents' actions.
We have just argued that  
one reason is that
doing this would sometimes enable the agents to solve a coordination problem.
Agents who will collaborate in an activity, such as moving a table or making a pizza, 
can sometimes individually make a  plan for all the agents' actions,
knowing that each agent's plan is sufficiently similar to the other agents' plans.
And sometimes each can rationally perform her part in her plan for all the agent's actions, knowing that the others will do likewise.%
\footnote{
As already mentioned, coordinating in this way does not require exercising shared agency because the planning can occur in parallel.
Of course,
	if some agents individually make a plan for all the agents' actions
	and then each rationally performs her part in her own plan,
	the upshot might be an exercise of shared agency.
But any such exercises of shared agency are a consequence of, not a requirement on, their individually making a plan for all the agents' actions.
}

Now recall Beatrice and Baldric (from Section \vref{sec:the_counterexample}).
We said earlier that  they each see the other's intentions and actions  as constraints to work around or opportunities to exploit only.
This is because neither agent makes a plan for both agents' actions and so neither conceives of both her own and the other's actions as parts of a single plan.%
\footnote{
We also stipulate that neither Ayesha nor Ahmed makes a plan for both of the agents' actions.
(We have not shown that Ayesha and Ahmed could not have done this; we merely stipulate that, as is perhaps natural to assume anyway, they do not.)
}
In constructing a case that contrasts with Beatrice and Baldric's we shall rely on the distinction between
a plan that includes both your own and another's actions
and 
a plan that merely exploits, and is constrained by, predictions about the other's actions.
This distinction matters independently of whether two such plans would result in different actions, as we shall argue in the next section.
It matters because 
making a plan for your own and another's actions 
	involves changing perspective.
That is, it involves conceiving of the other's actions not only as constraints to work around or opportunities to exploit, but as on a par with your own actions insofar as your actions and their actions are elements in a single plan directed to a single outcome.

@@

\section{Why Making One Plan or Two Matters}
The distinction between making a single plan and making two separate plans may initially seem too subtle to matter, 
especially as 
the separate planning processes may constrain each other.
Further, if any two separate plans can both be executed (not just each plan but both together), then they can be combined into a single plan.
The combined plan is simply to implement each of the two formerly separate plans. 
These reflections might misleadingly seem to 
indicate that there is no significant difference between making a single plan and making two separate plans.
However in this section we shall explain why the distinction between making a single plan and making two separate plans matters.
